---
title: "Work Abroad - No"
author: 
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---


# Centre and Periphery Distribution


```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
library(ggplot2)
library(MASS)

mydata <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/Rafi Barel/Data/english_data.csv", header=TRUE, sep=",")
startups = subset(mydata, character == "startup")
startups = subset(startups, abroad_group == "no")

qplot(region_group, data = startups) + 
  geom_histogram(fill="lightblue", color="grey50",binwidth=0.5) +
  ggtitle("Centre and Periphery Distribution")+ scale_x_continuous(name = "", breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)

```

# Characteristics {.tabset}


## Founder_CEO
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$founder_CEO)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = founder_CEO,binwidth=0.5) + 
  ggtitle("Is the current CEO is also the founder?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+
  scale_fill_discrete(name = "", labels = c("No", "Yes", "NA" ))

tbl = table(startups$region_group, startups$founder_CEO)
chisq.test(tbl)
```

## Hi-Tech Park
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$cluster_group)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = cluster_group,binwidth=0.5) + 
  ggtitle("Is it located in a Hi-Tech park?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+
  scale_fill_discrete(name = "", labels = c("In park", "Not in park", "NA" ))

```

## Established Year
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$established_group)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(established_group)  , binwidth=0.5)+ 
  ggtitle("When did it established?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+
  scale_fill_discrete(name = "", labels = c("Up to 2010", "Between 2011 to 2014", "Between 2015 to 2016", "After 2017" ))

```

## Employees
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$employees_group)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(employees_group)  , binwidth=0.5)+ 
  ggtitle("How many employees are working in the startup?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1) +
  scale_fill_discrete(name = "", labels = c("Up to 5", "6 to 10", "11 to 30", "35 or more" ))

```

# Activity Types {.tabset}

## Product/Service
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$product_group)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = product_group,binwidth=0.5) + 
  ggtitle("Is it a product or a service startup?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1) +
  scale_fill_discrete(name = "", labels = c("Product", "Service" ))

```

## Incremental/Radical
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$radical)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = radical,binwidth=0.5) + 
  ggtitle("Is it involved incremental or radical inovation?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1) +
  scale_fill_discrete(name = "", labels = c("Incremental", "Radical" ))

```

## R&D
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$r_d_based)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = r_d_based, binwidth=0.5) + 
  ggtitle("Is it a R&D based startup?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```

## Disruptive
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$disruptive)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = disruptive, binwidth=0.5) + 
  ggtitle("Would you define it as a disruptive inovation?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```

## Blue/Red ocean
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$blue_red)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = blue_red, binwidth=0.5) + 
  ggtitle("Would you define it as a red ocean strategy?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```

## Open/Close
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$open_close)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = open_close, binwidth=0.5) + 
  ggtitle("Would you define it as an open or close inovation?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+
  scale_fill_discrete(name = "", labels = c("Close", "Open" ))

```

# Productivity 

## Knowledge Productivity {.tabset}

### Patents
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$patent_group)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(patent_group), binwidth=0.5) + 
  ggtitle("Number of patents")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("None", "1 to 8", "10 or more" ))

```


## Last Year Growth {.tabset}

### Employment Change
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$employment_change)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(employment_change), binwidth=0.5) + 
  ggtitle("Last year employment change")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "")

```


### Sales Growth
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$sales_growth)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(sales_growth), binwidth=0.5) + 
  ggtitle("Last year sales change")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "")

```


### Improvement in Product, Process or Service
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$improvement)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(improvement), binwidth=0.5) + 
  ggtitle("Last year improvement in product, process or service")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "")

```

### Revenue from Selling Knowledge or Permits
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$knowledge)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(knowledge), binwidth=0.5) + 
  ggtitle("Have you sold any knowledge or permits in the last year?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```

### Exporting of Products or Services
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$exporting)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(exporting), binwidth=0.5) + 
  ggtitle("Have you export any products or services in the last year?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```

### Investing in Other Countries
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$investment)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(investment), binwidth=0.5) + 
  ggtitle("Did you invest in Other countries in the last year?")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```


## Others {.tabset}

### Trademark
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$trademark)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(trademark), binwidth=0.5) + 
  ggtitle("Trademark")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```


### Business Model
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$Business_model)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(Business_model), binwidth=0.5) + 
  ggtitle("Developing new business model")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```


### Organizational Model
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$Organizational_model)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(Organizational_model), binwidth=0.5) + 
  ggtitle("Developing new organizational model")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```



### generic Top Level Doman (gTLD)
```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
tbl = table(startups$region_group, startups$gtld)
text = paste("Chi-squared test's p-value:", round(chisq.test(tbl)$p.value,5))

qplot(region_group, data = startups, geom = "histogram", fill = as.character(gtld), binwidth=0.5) + 
  ggtitle("generic Top Level Doman (gTLD)")+ scale_x_continuous(name = text, breaks = c(0, 1), labels = c("Periphery","Center"))+
  stat_bin(aes(y=..count.., label=..count..), geom="text", binwidth=1, vjust=1.1)+ 
  scale_fill_discrete(name = "", labels = c("No", "Yes" ))

```